---
title: "Data Science Ethics Summer 2023"
output: 
  html_document:
    output_dir: "."
---

<br>

## Introduction to Website

Through my Statistics and Philosophy coursework, I have seen diverse approaches to grappling with issues in Data Science Ethics. For my Summer Undergraduate Research Project (SURP) through Pomona College, I am exploring the pedagogies of existing Data Science Ethics courses. Exploring the pedagogies for Data Science Ethics is a fantastic way for me to understand the central concepts in the field and the current conversations in Data Science Ethics research. Additionally, it also gives insights into interesting pedagogical questions such as: 

* Who is teaching Data Science Ethics courses?

* Which topics are most common within Data Science Ethics classes?

* How do Data Science Ethics courses, which are inherently interdisciplinary, cater to students with different philosophical and technical backgrounds? 

This website is a hub for my summer project on the teaching pedagogies of Data Science Ethics. By documenting my findings on this public website, I hope that others can also learn more about Data Science Ethics' teaching pedagogies or, just generally, the nascent field of Data Science Ethics.

<br>

## Syllabi Table 

The table below details the syllabi that I consulted during this project. A majority of them are undergraduate courses and include a reading list. Feel free to visit [Inside the Syllabi Notes](inside-syllabi.html) for in-depth notes on each course's learning goals and topics.


```{r echo = FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(DT)
library(knitr)
library(reactable)
library(reactablefmtr)
```

```{r echo = FALSE, message = FALSE, warning=FALSE}
syllabi <- tribble(
  ~title, ~institution, ~department, ~level, ~prereqs, ~instructor, ~intructor_discipline,  ~`link`, ~semester,
  ~list,"The Ethics of Data and Artificial Intelligence", "London School of Economics","Philosophy, Logic, and Scientific Method", "Undergraduate", "None", "Kate Vredenburgh, Ali Boyle, Alex Voorhoeve, Paola Romero", "Philosophy, Logic, and Scientific Method", '<a target="_top" href = "https://www.lse.ac.uk/ss-asset-library/course-outlines/2023/ME102-Course-Outline-2023.pdf" target = "_blank">Syllabus Link</a>', "Summer 2023", "Yes",
  "Data, Ethics, and Society", "Rice University", "Data Science", "Undergraduate", "None", "Elizabeth Petrick", "History", '<a target="_top" href = "https://www.google.com/url?sa=t&rct=j&q=&esrc=s&source=web&cd=&ved=2ahUKEwjBqtWbooD_AhUhIzQIHXWLD_c4ChAWegQIBhAB&url=https%3A%2F%2Festher.rice.edu%2Fselfserve%2F!bwzkpsyl.v_viewDoc%3Fterm%3D202120%26crn%3D23021%26type%3DSYLLABUS&usg=AOvVaw1zimMugXOdwaI0SYtmBHVE" target = "_blank">Syllabus PDF\n(automatically downloads)</a>', "Spring 2021", "Yes",
  "Human Contexts and Ethics of Data", "University of California, Berkeley", "Data Science (Cross-listed in History and STS)", "Undergraduate", "None", 'Margo Boenig-Lipstin,<br> Ari Edmundson', 'Margo Boenig-Lipstin: History<br>Ari Edmundson: Data Science', '<a target="_top" href = "https://docs.google.com/document/d/1aRSkK0FmyaWCIsFq4MCbTrP2yGmP_rTPQ9MJLzdwWnc/edit" target = "_blank">Syllabus Link</a>', "Spring 2020", "Yes",
  "Data Ethics", "University of California, San Diego", "Philosophy", "Undergraduate", "None", "David Danks", "Philosophy and Data Science", '<a target="_top" href = "https://philosophy.ucsd.edu/courses/course-syllabus/wi23/PHIL174.pdf" target = "_blank">Syllabus Link</a>', "Winter 2023", "Yes",
  "Computing, Ethics, and Society", "Northwestern University", "Computer Science", "Undergraduate", "None", "Sarah Van Wart", "Computer Science and Engineering", '<a target="_top" href = "https://nu-tech-ethics.github.io/winter2021/syllabus/" target = "_blank">Syllabus Link</a>', "Winter 2021", "Yes",
  "Ethical and Societal Issues in AI", "Cornell University", "Computer Science", "Undergraduate", "None", "Joseph Halpern,<br>Bart Selman", "Computer Science", '<a target="_top" href = "https://www.cs.cornell.edu/courses/cs4732/2017sp/" target = "_blank">Syllabus Link</a>', "Spring 2017", "Yes",
  "Ethics and Technology", "Swarthmore College", "First-year Seminar", "Undergraduate", "None", 'Ameet Soni,<br>Krista Karbowski Thomason','Ameet Soni: Computer Science<br> Krista Karbowski Thomason: Philosophy', '<a target="_top" href = "https://works.swarthmore.edu/cgi/viewcontent.cgi?article=1027&context=dev-dhgrants" target = "_blank">Syllabus Link</a>', "Spring 2019", "Yes",
  "Data Science Ethics", "Yale Univesity", "Statistics and Data Science", "Undergraduate", "Statistics and/or Data Analytics is Required,<br>Prior Coursework in AI/ML/Algorithms and Ethics/Philosophy is Useful", "Elisa Celis", "Statistics and Data Science", '<a target="_top" href = "https://datascienceethics.wordpress.com/the-course/syllabus/" target = "_blank">Syllabus Link</a>', "Spring 2019", "No",
  "Philosophical Foundations of Machine Learning", "Carnegie Mellon University", "Machine Learning", "Graduate/\nUndergraduate", "None", "Zachary Lipton", "Machine Learning and Operations Research", '<a target="_top" href = "https://github.com/acmi-lab/cmu-10721-philosophy-machine-intelligence" target = "_blank">Syllabus Link</a>', "Spring 2023", "Yes",
  "Ethics and Policy in Data Analytics", "Carnegie Mellon University", "Information Systems and Public Policy", "Graduate", "Familiarity with Data Analytics Pipeline is Recommended", "David Danks, Sina Fazelpour", 'David Danks: Data Science and Philosophy<br>Sina Fazelpour: Computer Science and Philosophy', '<a target="_top" href = "https://www.heinz.cmu.edu/current-students/courses/94-836/2238/" target = "_blank">Syllabus Link</a>', "Spring 2021", "Yes",
  "Ethics in AI", "", "Philosophy", "Graduate/\nUndergraduate", "Prior Coursework in Moral/Political Philosophy and Logic/Statistics is Useful", "Liam Kofi Bright", "Philosophy", '<a target="_top" href = "https://philpeople.org/public_cache/file?content_type=application%2Fpdf&key=z1d1wj8yk9ztczwt4d9wspqbl6qb" target = "_blank">Syllabus Link</a>', "Spring 2023", "Yes",
  "Ethics and Policy in Data Science", "Cornell University", "Information Sciences", "Graduate/\nUndergraduate", "None", "Solon Barocas", "Information Science (and Principle Researcher at Microsoft)", '<a target="_top" href = "https://docs.google.com/document/d/1GV97qqvjQNvyM2I01vuRaAwHe9pQAZ9pbP7KkKveg1o/edit" target = "_blank">Syllabus Link</a>', "Fall 2017", "Yes",
  "The Ethics and Governance of Artificial Intelligence", 'Massachusetts Institute of Technology,<br>Harvard University', "Cross-Disciplinary", "Graduate", "None", 'Joi Ito,<br>Jonathan Zittrain', 'Joi Ito: Practice in Media Arts and Science<br>Jonathon Zittrain: International Law, Computer Science, and Public Policy', '<a target="_top" href = "https://dam-prod.media.mit.edu/x/2018/02/07/Ethics%20and%20Governance%20of%20AI%20S18%20.pdf" target = "_blank">Syllabus PDF\n(automatically downloads)</a>', "Spring 2018", "Yes",
  "Ethics, Public Policy, and Technological Change", "Stanford University", "Computer Science", "Undergraduate", "None", "Rob Reich, Mehran Sahami, Jeremy Weinstein", 'Rob Reich: Political Science<br>Mehran Sahami:Computer Science<br>Jeremy Weinstein: Computer Science', '<a target="_top" href = "https://web.stanford.edu/class/cs182/" target = "_blank">Syllabus Link</a>', "Winter 2023","Yes",
  "Ethics, Data, and Technology", "University of Florida", "Philosophy", "Undergraduate", "None", "David Gray Grant", "Philosophy", '<a target="_top" href = "https://phil.ufl.edu/wp-content/uploads/sites/145/2022/01/PHI3681-Grant-Syllabus-2021-28-12.pdf" target = "_blank">Syllabus Link</a>', "Spring 2022", "Yes",
  "Special Topics in Data Science:<br>
Responsible Data Science", "New York University", "Data Science", "Undergraduate", "Introduction to Data Science or <br> Introduction to Computer Science", "Julia Stoyanovich", "Data Science, Computer Science, and Engineering", 
  '<a target="_top" href = "https://dataresponsibly.github.io/courses/spring19/" target = "_blank">Syllabus Link</a>', "Spring 2019", "Yes"
  )
```

```{r echo = FALSE, message = FALSE, warning=FALSE}
reactable(syllabi, elementId = "syllabi-table",
          columns = list(title = colDef("Course Title", html = TRUE),
                                                    institution = colDef("Institution",
                                                                         minWidth = 120,
                                                                         html = TRUE), 
                                                    department = colDef("Department",
                                                                        minWidth = 120,
                                                                        html = TRUE), 
                                                    level = colDef("Course Level",
                                                                   minWidth = 130,
                                                                   html = TRUE),
                                                    prereqs = colDef("Prerequesites",
                                                                     minWidth = 130,
                                                                     html = TRUE),
                                                    instructor = colDef("Instructor(s)",
                                                                        minWidth = 120,
                                                                        html = TRUE),
                                                    intructor_discipline = colDef("Instructor's Discpline",
                                                                                  minWidth = 130,
                                                                                  html = TRUE),
                                                    link = colDef("Syllabus Link", html = TRUE,
                                                                  minWidth = 130),
                                                    semester = colDef("Syllabus' Term"), 
                                                    list = colDef("Reading List Included?")), 
          highlight = TRUE,
          searchable = TRUE,
          showSortable = TRUE,
          showPagination = TRUE,
          filterable = TRUE,
          resizable = TRUE,
          fullWidth = FALSE,
           theme = reactableTheme(
             highlightColor = "#F0EDD1",
             style = list(
      fontFamily = "-apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif",
      fontSize = '14px',
      marginLeft = "-80px",
      marginRight="40px"
    )))
