---
title: "Privacy Readings"
output: html_document
bibliography: bibliographies/Privacy-readings.bib
link-citations: true
csl: bibliographies/apa-6th-edition.csl
nocite: '@*'
---


----

## Primary Privacy Readings

----

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(reactable)
library(reactablefmtr)
```

```{css}
h1 {
  text-align: left;
}

.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
    z-index: 2;
    color: #fff;
    background-color:  #877e2c;
    border-color:  #877e2c;
}
```


```{r}
privacy <- tribble(~Title, ~Reading_One, ~Summary, ~Tags,
                                        "Privacy\n(Stanford Encyclopedia of Philosophy)",
                   '<span class="citation">DeCew (<a href="#ref-sep-privacy"
role="doc-biblioref">2018</a>)</span>', 
                   ".", 
                   "<a href='consent.html'>Primer</a>,",
"Why Privacy is Important",
'<span class="citation">Rachels (<a
href="#ref-why-privacy-imp" role="doc-biblioref">1975</a>)</span>',
".",
"<a href='consent.html'>Primer</a>, <a href='consent.html'>Case Study</a>,",
"Why We Care about Privacy",
'<span class="citation"> McFarland (<a href="#ref-why-care-privacy"
role="doc-biblioref">2012</a>)</span>',
".",
"<a href='consent.html'>Primer</a>, <a href='consent.html'>Case Study</a>,",
"The Right to Privacy",
'<span class="citation">Thomson (<a
href="#ref-right-privacy" role="doc-biblioref">1975</a>)</span>',
".",
"<a href='consent.html'>Primer</a>, <a href='consent.html'>Case Study</a>,",
                   "A Modern Pascal's Wager for Mass Electronic Surveillance",
                    '<span class="citation">Danks (<a
href="#ref-Danks-privacy" role="doc-biblioref">2014</a>)</span>',
                    "", 
"<a href='consent.html'>Law</a>,",
"Privacy and Paternalism: The Ethics of Student Data Collection",
'<span class="citation">Miller &amp; Wertheimer (<a
href="#ref-ethics-consent" role="doc-biblioref">2010</a>)</span>',
".",
"<a href='consent.html'>Primer</a>,",
"What’s Wrong with Automated Influence?",
'<span class="citation">Benn &amp; Lazar (<a href="#ref-automated-influence"
role="doc-biblioref">2021</a>)</span>',
".",
"<a href='consent.html'>Policy</a>, <a href='consent.html'>Law</a>,",
"Privacy and Human Behavior in the Age of Information",
'<span class="citation">Acquisti, Brandimarte, &amp; Loewenstein (<a
href="#ref-privacy-behavior" role="doc-biblioref">2015</a>)</span>',
".",
"<a href='consent.html'>Primer</a>, <a href='consent.html'>Case Study</a>,",
"From Individual to Group Privacy in Big Data Analytics",
'<span class="citation">Mittelstadt (<a href="#ref-individual-group"
role="doc-biblioref">2017</a>)</span>',
".",
"<a href='consent.html'>Primer</a>, <a href='consent.html'>Case Study</a>,",
"Big Data's End Run around Procedural Privacy Protections",
'<span class="citation">Barocas &amp; Nissenbaum (<a href="#ref-end-procedural"
role="doc-biblioref">2014b</a>)</span>',
".",
"<a href='consent.html'>Primer</a>, <a href='consent.html'>Case Study</a>,",
"Why 'Anonymous' Data Sometimes Isn't",
'<span class="citation">Schneier
(<a href="#ref-anonymous-data"
role="doc-biblioref">2007</a>)</span>',
".",
"<a href='consent.html'>Primer</a>, <a href='consent.html'>Case Study</a>,",
)
```

```{r}
reactable(privacy,
          columns = list(Title = colDef("Title", html = TRUE, align = "center", vAlign = "center"),
            Reading_One = colDef("Reference", html = TRUE, minWidth = 100, align = "center", vAlign = "center"),
                         Summary = colDef("Summary", html = TRUE, minWidth = 250),
                         Tags = colDef("Tags", html = TRUE, width = 90)),
          resizable = TRUE,
          highlight = TRUE,
          pagination = FALSE,
          showSortable = TRUE,
          searchable = TRUE,
          theme = reactableTheme(
             highlightColor = "#F0EDD1",
             style = list(
      fontFamily = "-apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif",
      fontSize = '14px')
          )
)
```

----

## Additional Privacy Readings

----


* [Privacy and Human Behavior in the Age of Information](https://www.cmu.edu/dietrich/sds/docs/loewenstein/PrivacyHumanBeh.pdf)

* [Philosophy of Privacy and Digital Life](https://papers.ssrn.com/sol3/papers.cfm?abstract_id=4022657#:~:text=The%20most%20comprehensive%20philosophy%20of,live%20digitally%20driven%20and%20digitally)

* [Nothing to Hide](https://drive.google.com/file/d/1bhtSpwDlTlZSJMXIH1f-Kqz8U6lVo2-7/view)

* [It’s Not Privacy, and It's Not Fair](https://www.stanfordlawreview.org/online/privacy-and-big-data-its-not-privacy-and-its-not-fair/)

* [Digital Reputation in an Era of Runaway Data](https://www.degruyter.com/document/doi/10.4159/harvard.9780674736061.c3/html?lang=en)

* [Surveillance and Capture: Two Models of Privacy](https://www.tandfonline.com/doi/abs/10.1080/01972243.1994.9960162)

* [The Surveillance Society](https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1460-2466.1989.tb01040.x)

* [Recommender Systems and Their Ethical Challenges](https://link.springer.com/article/10.1007/s00146-020-00950-y)

* [Why ‘I Have Nothing to Hide’ is the Wrong Way to Think About Surveillance](https://www.wired.com/2013/06/why-i-have-nothing-to-hide-is-the-wrong-way-to-think-about-surveillance/)

* [Can a Set of Equations keep U.S. Census Data Private?](https://www.science.org/content/article/can-set-equations-keep-us-census-data-private)

----

## Primary Privacy Readings' References

----